---
title: 'Task 2: explore prior knowledge network'
author: "A. Gabor"
date: "6/28/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(OmnipathR)
library(tibble)
library(dplyr)

```



## Download post-translational modifications:

```{r}
# 
ptms = import_omnipath_enzsub(resources=c("PhosphoSite", "SIGNOR")) %>% as_tibble()
head(ptms,10)
```

Enzyme-substrate information could be useful when measurements are antibody based 
that recognise the phosphorylaition of certain p-sites of the proteins. 

Enz-substr interactions are often limited (total 14k interactions). 



## Download protein-protein interactions



```{r}
interactions = import_omnipath_interactions() %>% as_tibble()
head(interactions,10)
```

What are the interactions of MAPK1? 

```{r}
interactions %>% dplyr::filter(source_genesymbol == "MAPK1") %>% print_interactions()
```

## Convert to graph to search for neighbours
```{r}
OPI_g = interaction_graph(interactions = interactions)
```



Let's say we want to connect two nodes of the network and we need evidence: 
Use shortest path to find connections. 
```{r}

sp_Tyro2STAT3 <- shortest_paths(OPI_g,from = "TYRO3",to = "STAT3",
   output = 'epath')


print_path_es(shortest_paths(OPI_g,from = "TYRO3",to = "STAT3",
   output = 'epath')$epath[[1]],OPI_g)

```




```{r}
sessionInfo()
```

